### 2014-01-22 intro.tex
Make it compile
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Not really dynamically forced isolation
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

In this paper, we describe a simple but general methodology for using
isolation of \emph{execution contexts}, e.g.\ an instance of the
JavaScript engine, in order to add information-flow control to an
existing language.  This is a very practical approach, as there are many
languages which have built-in capabilities for dynamically enforced
strong isolation (i.e. Web Workers).  To validate this methodology, we
describe its application to Haskell (LIO), to JavaScript (Browbound), to
C (HipStar) and to Java (Aeolis).  The essential idea is to combine the
formal models of the source language and a minimal IFC language, using
the embedding technique described in Matthews and Findler '07.

@@

>>>>

In this paper, we describe a simple but general methodology for using
isolation of \emph{execution contexts}, e.g.\ an instance of the
JavaScript engine, in order to add information-flow control to an
existing language.  This is a very practical approach, as there are many
languages which have built-in capabilities for strong isolation by
forking an execution context (i.e. Web Workers).  To validate this
methodology, we describe its application to Haskell (LIO), to JavaScript
(Browbound), to C (HipStar) and to Java (Aeolis).  The essential idea is
to combine the formal models of the source language and a minimal IFC
language, using the embedding technique described in Matthews and
Findler '07.

@@

The organization of the paper is as follows: first, we describe how to
add information flow control to JavaScript, showing the general outline of
our procedure. Next, we describe the procedure in generality.  Finally, we
apply the procedure to a number of systems.
